Updating Projection Data and Merging with ITQ

### 2018-11-11 lab_notebook.Rmd
updated projection data merged ITQ data simplified data frame for regressions

#RAM data wrangling
```{r}
ram <- select(timeseries_values_views, "stocklong", "year", "TBbest", "TCbest", "BdivBmsypref", "UdivUmsypref")

colnames(ram) <- c( "CommName", "Year", "Biomass", "Catch", "BvBmsy", "FvFmsy")

ram_2012 <- ram %>%
  filter(Year > "2012") 
##this wont work because projection data has projected out past 2012. need to UPDATE

#updated 
projection_ram <- bind_rows(list(projection_data, ram_2012))

@@

#check that is worked
projectramcheck <- join_project_ram %>%
  filter(Year == "2013") %>%
  select("IdOrig", "Year", "CommName")

unite_projection_commname <- projection_data %>% 
  unite(name_year, CommName, Year, sep = "-")
unite_ram_commname <- ram %>% 
  unite (name_year, CommName, Year, sep = "-")
join_project_ram_2 <- join(unite_projection_commname, unite_projection_commname, by = "name_year", type = "full")

@@

#Total number of species with stocks
#Number of stocks with ITQs implemented
```{r}
IdOrig <- unique(ITQ_projection$IdOrig)
IdOrig
#337 species total

@@

IdOrig_implemented <- unique(ITQ_projection_implemented$IdOrig)
IdOrig_implemented
#115 species with ITQ implemented
```

>>>>

#RAM data wrangling
```{r}
ram <- timeseries_values_views %>%
  select("stocklong", "year", "TBbest", "TCbest", "BdivBmsypref", "UdivUmsypref") %>%
  add_column("RAM")

colnames(ram) <- c( "CommName", "Year", "Biomass", "Catch", "BvBmsy", "FvFmsy", "DBase")

#ram_2012 <- ram %>%
#  filter(Year > "2012") 
##this wont work because projection data has projected out past 2012. need to UPDATE

#updated 
#projection_ram <- bind_rows(list(projection_data, ram_2012))

@@

projectramcheck <- filter(join_project_ram, IdOrig == "NA")
#returns no rows with NA, could still be right if updated projected

#Checking to see if better way to do join
# end up with WAY to many rows, something is off
#unite_projection_commname <- projection_data %>% 
#  unite(name_year, CommName, Year, sep = "-")
#unite_ram_commname <- ram %>% 
#  unite (name_year, CommName, Year, sep = "-")
#join_project_ram_2 <- join(unite_projection_commname, unite_projection_commname, by = "name_year", type = "left")

match_project_ram <- match(projection_data, ram)

@@

#Total number of species with stocks
#Number of stocks with ITQs implemented
```{r}
IdOrig <- unique(ITQ_projection$SciName)
IdOrig
#1228 species total

@@

IdOrig_implemented <- unique(ITQ_projection_implemented$SciName)
IdOrig_implemented
#80 species with ITQ implemented
```

### 2018-11-11 scripts/projection_ITQ.Rmd
updated projection data merged ITQ data simplified data frame for regressions

IdOrig_implemented <- unique(ITQ_projection_implemented$IdOrig)
IdOrig_implemented
#115 species with ITQ implemented
```

>>>>

IdOrig_implemented <- unique(ITQ_projection_implemented$SciName)
IdOrig_implemented
#80 species with ITQ implemented
```

#Simplified Projection Data
```{r}

ITQ_projection_simple <- ITQ_projection %>%
  select("Country", "Year", "CommName", "SciName", "SpeciesCat", "CatchShare", "Catch", "Biomass", "BvBmsy", "FvFmsy","MSY", "Price", "g", "k", "c", "phi", "yearitq", "itq_now", "turf", "programstart")

```
